Sailing the High Seas: A Christian Exploration of Piracy

### 2024-04-28 paper.tex
Add abstract

\begin{document}
\begin{refsection}
\maketitle
\epigraph{%
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.%
}{Thomas Jefferson~\cite{barlow:wine}}

>>>>

\begin{document}
\begin{refsection}
\maketitle

\epigraph{%
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.%
}{Thomas Jefferson~\cite{barlow:wine}}

\begin{abstract}
  This study is a comprehensive study of piracy, particularly in the digital
  realm, from a Christian perspective. The paper delves into the ethical, legal,
  and moral implications of piracy, acknowledging both its potential benefits
  and drawbacks. The authors argue that piracy can promote equal access to
  information, challenge oppressive regimes, and protect privacy. However, they
  also highlight the risks associated with piracy, such as the distribution of
  dangerous or illegal content and its negative economic impact. The paper
  concludes with a call for a nuanced Christian response to piracy, emphasizing
  the importance of respecting authority and considering the potential
  consequences of piracy while considering the staying power and benefits of
  piracy-promoting tools and practices. This work encourages a thoughtful
  exploration of piracy, rather than a hasty dismissal or acceptance.
\end{abstract}
